\documentclass{ximera}

\input{../preamble.tex}

\title[Prerequisite Videos: ]{Fundamentals of Factoring}

\outcome{Understand common techniques in factoring, such as common terms and factoring quadratic polynomials.}

\begin{document}
\begin{abstract}
  We go through common prerequisite topics about fundamentals of factoring. 
  We look at common factors and factoring quadratic polynomials.
\end{abstract}
\maketitle

The following videos will cover topics about functions and their graphs:

%% Factoring Polynomials Warning

\textbf{Factoring Video Warning!}
\youtube{TM7k2L8_EiE}



%% Introduction and Question 1
\textbf{Introduction and Question 1: Factoring With Common Factors}
\begin{question}
%% Labeling this expandable option
\begin{flushright}
{\color{blue}(\emph{Click the arrow to the right to see the Introduction video and first question.})}
\end{flushright}
\begin{center}
\begin{expandable}
\youtube{TUbeYSyZn9c}
%% Multiple Choice Question 1
{\color{blue}(\emph{Click the arrow to the right to see the answers 
to the question posed at the end of the video.})}
\begin{expandable}
Which of the following ways does $2x^2 + 6x$ factor?
\begin{multipleChoice}
\choice[correct]{$2x(x+3)$}
\choice{$x+3$}
\choice{$(2x+1)(x+3)$}
\choice[correct]{$12x^3$}
\end{multipleChoice}
%% Example 1
\begin{flushright}
{\color{blue}(\emph{Click the arrow to the right to see an example.})}
\end{flushright}
\begin{expandable}
Example 1
\youtube{C8R35E7YSRs}

Checking The Answer
\youtube{T2CSjylE7tQ}
\end{expandable}
\end{expandable}
\end{expandable}
\end{center}
\end{question}


















\end{document}